---
title: "Homework 1"
author: "Wei Wei"
date: '2018-09-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 (Chapter 2, #1, 8 marks)

(a) Flexiable method is better,When the the number of predictors is large, it also decreases the risk of overfitting.

(b) Inflexible method is better, it reduced the risk of overfitting when the observations is small.

(c)flexiable method is better,inflexiable method is having trouble to deal with non-linear relationships.

(d)inflexiable method is better, it can reduce the risk of overfitting the noise in this relationship.

## Question 2 (Chapter 2, #2, 6 marks)

(a) regression and inference, since we are interested in the factors affect CEO salary, and the slary is a continous varible, n=500(firms),p=3 (profit, employees, industry)

(b) classification and prediction, since the product will be either success or failure, n=20(products) p=13(price, budget, competition price, 10 other variables)

(c)regression and prediction,  since we are interested in prediction the % change in exchange rate, the % change is a continous variable, n=52(weeks), p=3(% change in US, British and German market)

## Question 3 (Chapter 2, #9, 8 marks)

```{r}
library(ISLR) # use install.packages("ISLR") to install
data(Auto)
head(Auto)
```

(a)
       mpg         cylinders     displacement   horsepower   
  Min.   : 9.0   Min.   :3.00   Min.   : 68   Min.   : 46.0  
  1st Qu.:17.0   1st Qu.:4.00   1st Qu.:105   1st Qu.: 75.0  
  Median :22.8   Median :4.00   Median :151   Median : 93.5  
  Mean   :23.4   Mean   :5.47   Mean   :194   Mean   :104.5  
  3rd Qu.:29.0   3rd Qu.:8.00   3rd Qu.:276   3rd Qu.:126.0  
  Max.   :46.6   Max.   :8.00   Max.   :455   Max.   :230.0  
                                                             
      weight      acceleration       year        origin    
  Min.   :1613   Min.   : 8.0   Min.   :70   Min.   :1.00  
  1st Qu.:2225   1st Qu.:13.8   1st Qu.:73   1st Qu.:1.00  
  Median :2804   Median :15.5   Median :76   Median :1.00  
  Mean   :2978   Mean   :15.5   Mean   :76   Mean   :1.58  
  3rd Qu.:3615   3rd Qu.:17.0   3rd Qu.:79   3rd Qu.:2.00  
  Max.   :5140   Max.   :24.8   Max.   :82   Max.   :3.00  
                                                           
     name    
  amc matador       :  5  
  ford pinto        :  5  
  toyota corolla    :  5  
  amc gremlin       :  4  
  amc hornet        :  4  
  chevrolet chevette:  4  
  (Other)           :365
the name and origin are qualitative, mpg, cylinders, displacement, horsepower, weight,acceleration and year are quantitative.
(b)

```{r}
# Hints:
#   with(Auto,range(mpg)); with(Auto,range(cylinders)), etc.
# or you can use apply() on subsets of columns
apply(Auto[,1:5],MARGIN=2,FUN=range)
# or we can name the output of range and call apply
myr <- function(x) {
  out <- range(x)
  names(out) <- c("min","max")
  out
}
apply(Auto[,1:5],MARGIN=2,FUN=myr)
```
       mpg cylinders displacement horsepower weight acceleration year
 [1,]  9.0         3           68         46   1613          8.0   70
 [2,] 46.6         8          455        230   5140         24.8   82


(c)

```{r}
# Hint
meansd <- function(x) {
  out<-c(mean(x),sd(x))
  names(out) <- c("mean","SD")
  out
}
```
       mpg cylinders displacement horsepower weight acceleration year
 [1,] 23.0       5.5          190        100   3000         16.0 76.0
 [2,]  7.8       1.7          100         38    850          2.8  3.7

(d)

```{r}
# Hint:
AutoSubset <- Auto[c(1:9,86:nrow(Auto)),1:7]
```
        mpg cylinders displacement horsepower weight acceleration  year
 min  11.00      3.00        68.00      46.00 1649.0         8.50 70.00
 max  46.60      8.00       455.00     230.00 4997.0        24.80 82.00
 mean 24.40      5.37       187.24     100.72 2936.0        15.73 77.15
 sd    7.87      1.65        99.68      35.71  811.3         2.69  3.11

(e)
I made the scatterplots of horsepower vs weight, mpg vs weight, mpg vs cylinders, those graphs shown the linear trends,horsepower increase as weight increase, mpg decrease as cylinders increase,acceleration decrease as displacement increase. 
(f)
